Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-18 CAV2018/paper.tex
+ authors (in the order used by Dario on easychair)
revise intro to compare CEGIS-OR to the abstraction refinement step in CAV'17

\author{}{}{}{}{}

%\email{alessandro.abate@cs.ox.ac.uk}
%\email{dario.cattaruzza@cs.ox.ac.uk}
%\author{Cristina David}\email{cristina.david@cs.ox.ac.uk}
%\email{kroening@cs.ox.ac.uk}

@@

\authorrunning{}

@@

We use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{jha-icse10,
DBLP:conf/asplos/Solar-LezamaTBSS06} approach, which we enhance with
abstraction refinement and optimization resulting in the novel CEGIS-OR
(CEGIS with Optimization and Refinement).  This design uses an iterative
process where each iteration performs inductive generalization based on
counterexamples provided by a verification oracle.  Essentially, the
inductive generalization uses information about a limited number of inputs
to make claims in the form of candidate solutions about all the possible
inputs.  By~using abstraction refinement, CEGIS-OR allows us to handle
complex systems, which are initially represented by coarse abstractions that
only get refined on demand.  Consequently, solutions that do not require a
high level of precision are obtained fast.  Since the use of coarse
abstractions may result in low-quality candidate solutions (i.e., candidates
that fail the specification on a very large number of inputs), we use
optimization techniques after each inductive generalization phase to improve
the produced candidates.  In particular, our optimization procedure reduces
the size of the reach space of the closed loop system, while maintaining
other dynamical properties of interest (safety, stability, and response
time).

>>>>

\author{Dario Cattaruzza}{University of Oxford}{}{}{}
\author{Cristina David}{University of Cambridge, Diffblue}{}{}{}
\author{Alessandro Abate}{University of Oxford}{}{}{}
\author{Daniel Kroening}{University of Oxford, Diffblue}{}{}{}

\authorrunning{Cattaruzza, David, Abate, Kroening}

%\email{alessandro.abate@cs.ox.ac.uk}
%\email{dario.cattaruzza@cs.ox.ac.uk}
%\email{cristina.david@cs.ox.ac.uk}
%\email{kroening@cs.ox.ac.uk}

@@

@@

We use a CounterExample-Guided Inductive Synthesis
(CEGIS)~\cite{jha-icse10, DBLP:conf/asplos/Solar-LezamaTBSS06}
approach, which we enhance with abstraction refinement and
optimization resulting in the novel CEGIS-OR (CEGIS with Optimization
and Refinement).  This design uses an iterative process where each
iteration performs inductive generalization based on counterexamples
provided by a verification oracle.  Essentially, the inductive
generalization uses information about a limited number of inputs to
make claims in the form of candidate solutions about all the possible
inputs.  Similar to \cite{DBLP:conf/cav/AbateBCCDKKP17}, the use of
abstraction refinement is meant to allow CEGIS-OR to handle complex
systems, which are initially represented by coarse abstractions that
only get refined on demand.  However, the problem we observed with
this approach is that the use of coarse abstractions often results in
low-quality candidate solutions (i.e., candidates that fail the
specification on a very large number of inputs) and, consequently, there
are very few solutions obtained at such low levels of precision.
%% Consequently, solutions that do not require a
%% high level of precision are obtained fast.  Since the use of coarse
%% abstractions may result in low-quality candidate solutions (i.e., candidates
%% that fail the specification on a very large number of inputs),
In this paper, we address this problem by using 
optimization techniques after each inductive generalization phase to improve
the produced candidates.  In particular, our optimization procedure reduces
the size of the reach space of the closed loop system, while maintaining
other dynamical properties of interest (safety, stability, and response
time).
Consequently, solutions that do not require a
high level of precision can indeed be obtained fast.
